External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings. The first dataset provided in \cite{ncwebsite} includes 20 real noisy images collected under uncontrolled outdoor environment. This dataset does not have ``ground truth" images and hence the objective measurements can not be performed. In order to evaluate the compared methods on quantitative measures, we perform experiments on the second dataset provided in \cite{crosschannel2016}. It includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. Since the 17 images are too large (of size about $7000\times5000\times3$) and share repetitive contents, the authors in \cite{crosschannel2016} performed comparison on 15 cropped images (of size $512\times 521\times3$). To evaluate the compared methods on more samples, we cropped the 17 large images from \cite{crosschannel2016} into 60 smaller images (of size $500\times 500\times3$) including different contents. Some samples are shown in Figure \ref{fig4}. Note that the noise in our cropped 60 images used in \cite{crosschannel2016} are different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are taken in different shots.

>>>>

We evaluate the proposed method on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings.

The first dataset is provided in \cite{ncwebsite}, which includes 20 real noisy images collected under uncontrolled outdoor environment. Since there is no ``ground truth" of the noisy images, the objective measures such as PSNR cannot be computed on this dataset.

The second dataset is provided in \cite{crosschannel2016}, which includes noisy images of 17 static scenes. The noisy images were collected under controlled indoor environment. Each scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. Since the image size is very large (about $7000\times5000$) and the 17 scenes share repetitive contents, the authors of \cite{crosschannel2016} cropped 15 smaller images (of size $512\times512$) to perform experiments. To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments. Some samples are shown in Figure \ref{fig4}. Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.
